### 2021-06-24 Supplementary_Material/Supplementary_Material.Rmd
edits on fig s2

@@

@@

@@

>>>>

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_complete_cases.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest_complete_cases.rds")

@@

#Invert axes
#PC$S[,1] <- -PC$S[,1]
PC$S[,2] <- -PC$S[,2]

pc3 <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.015, 0.03, 0.07), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
    scale_alpha(guide = 'none')

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,5.2,5,5.25,6.3,6)), y = -(PCAloadings$PC2*c(4,4.75,4,4.5,5,5.5)+c(0,0,0,0,-0.04,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
